Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-11-11 Methods-and-Results.Rmd
typos

Based on our main hypotheses, the aim of our first study was to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. To this aim, we recruited recent migrants to the Netherlands for an intensive longitudinal survey. Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days). Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data description is available in Online Supplementary Material A).

@@

\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, the daily experience sampling measurements, and a concluding post-measurement. After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration. Over the next thirty days, participants were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup. General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}. The response rates were approximately equal during mornings (\textit{n} = `r format(sum(workerSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(workerSampleInfo$afternoonN), big.mark=",")`) and most measurements were completed within four hours of the invitation. After the final day of experience sampling measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement. All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable. To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}. Participants then rated their attitude on a continuous slider scale from “very cold – 0” through “no feeling – 50” to “very warm – 100”. Both the question phrasing as well as the tick labels were consistent with large-scale panel surveys \citep[e.g.,][]{DeBell2010}.

@@

\subsubsection{Contact Hypothesis}
Using a multilevel regression, we find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.

@@

The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived contact quality during intergroup contacts. However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop-up explanations described later). The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis. Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

\subsubsection{Participants} We recruited `r nrow(studentSampleInfo)` international students using a local participant pool. We specifically targeted non-Dutch students, who had recently arrived in the Netherlands. Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon). With this design, we again aimed at receiving 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(studentSampleInfo$dailiesN), big.mark=",")`). As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results. Participants were compensated for their participation with partial course credits --- depending on their participation. The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(studentSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(studentSampleInfo$age),2), nsmall=2)`, `r nrow(studentSampleInfo %>% filter(gender == "women"))` women). The sample fairly accurately describes the local population of international students.

\subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements. The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.  General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in). The response rates were approximately equal during mornings (\textit{n} = `r format(sum(studentSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(studentSampleInfo$afternoonN), big.mark=",")`). All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner). Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction. It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are import to you in the moment. It really depends on your subjective experience of the interaction.". Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).

\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality was identical to Study 1.

@@

\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement. The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.  General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more). The response rates were approximately equal during mornings (\textit{n} = `r format(sum(medicalSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(medicalSampleInfo$afternoonN), big.mark=",")`). All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to Study 1.

\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.

@@

\subsubsection{Contact Hypothesis}
In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}). Thus, in our third data set we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.

@@

We tested the impact of Allport's conditions in the same manner as we tested our core needs model. In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`). Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}). These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.

@@

To test whether Allport's conditions or the core need fulfillment were better at predicting outgroup attitudes, we first assessed relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predicted the same variance in outgroup attitudes. When comparing the model selection indices, we found that the fulfillment of the situational core need indeed performed slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$). Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}). This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.

\section{Robustness, Stability, and Embeddeness across Studies}

@@

\subsection{Contact key need content}
Finally, we used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis. However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyse these qualitative responses in a traditional qualitative content analysis. We instead relied on recent machine learning advances within the natural language processing domain. For our analysis we used the BERT language model. BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows. In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents. We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics. The higher number of topics allowed us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%). A full write up of the topic modeling process is available in Online Supplemental Material B.

In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance. Opposing the task and work oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment. Additionally, some clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself. Similarly, socializing and celebrations were also explicit social needs (incl., parties). This also included a subtopic of spiritual, religious, and otherwise transcendental needs (incl. meditation, prayer, religious services). Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned informational needs more generally (e.g., seeking answers, bureaucratic information). A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific to contact through the medical and public health system. This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly highlighted interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals). Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members. Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living). In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

>>>>

Based on our main hypotheses, the aim of our first study was to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. To this aim, we recruited recent migrants to the Netherlands for an intensive longitudinal survey. Data were collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days). Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data description is available in Online Supplementary Material A).

@@

\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, the daily experience sampling measurements, and a concluding post-measurement. After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration. Over the next thirty days, participants were invited twice a day (at 12pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup. General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}. The response rates were approximately equal during mornings (\textit{n} = `r format(sum(workerSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(workerSampleInfo$afternoonN), big.mark=",")`) and most measurements were completed within four hours of the invitation. After the final day of experience sampling measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement. All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement, we asked all participants about their current attitudes towards the Dutch – our main dependent variable. To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}. Participants then rated their attitude on a continuous slider scale from “very cold – 0” through “no feeling – 50” to “very warm – 100”. Both the question phrasing as well as the tick labels were consistent with large-scale panel surveys \citep[e.g.,][]{DeBell2010}.

@@

\subsubsection{Contact Hypothesis}
Using a multilevel regression, we find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data, we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.

@@

The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived contact quality during intergroup contacts. However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop-up explanations described later). The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis. Data were collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

\subsubsection{Participants} We recruited `r nrow(studentSampleInfo)` international students using a local participant pool. We specifically targeted non-Dutch students, who had recently arrived in the Netherlands. Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon). With this design, we again aimed at receiving 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(studentSampleInfo$dailiesN), big.mark=",")`). As with the previous study, this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results. Participants were compensated for their participation with partial course credits --- depending on their participation. The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(studentSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(studentSampleInfo$age),2), nsmall=2)`, `r nrow(studentSampleInfo %>% filter(gender == "women"))` women). The sample fairly accurately describes the local population of international students.

\subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements. The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for 30 days.  General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in). The response rates were approximately equal during mornings (\textit{n} = `r format(sum(studentSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(studentSampleInfo$afternoonN), big.mark=",")`). All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Psychological Needs}For the core situational need, we asked participants in an open-ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner). Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction. It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are important to you in the moment. It really depends on your subjective experience of the interaction.". Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).

\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality were identical to Study 1.

@@

\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement. The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for 30 days.  General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more). The response rates were approximately equal during mornings (\textit{n} = `r format(sum(medicalSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(medicalSampleInfo$afternoonN), big.mark=",")`). All key variables for this study were part of the short experience sampling surveys.

@@

\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality were identical to Study 1.

\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer, as in studies one and two.

@@

\subsubsection{Contact Hypothesis}
In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}). Thus, in our third data set, we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.

@@

We tested the impact of Allport's conditions in the same manner as we tested our core needs model. In the multilevel models, we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`). Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}). These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.

@@

To test whether Allport's conditions or the core need fulfillment were better at predicting outgroup attitudes, we first assessed relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predicted the same variance in outgroup attitudes. When comparing the model selection indices, we found that the fulfillment of the situational core need indeed performed slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$). Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar-sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}). This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.

\section{Robustness, Stability, and Embeddedness across Studies}

@@

\subsection{Contact key need content}
Finally, we used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis. However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyze these qualitative responses in a traditional qualitative content analysis. We instead relied on recent machine learning advances within the natural language processing domain. For our analysis, we used the BERT language model. BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key element of many natural language processing workflows. In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents. We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics. The higher number of topics allowed us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%). A full write-up of the topic modeling process is available in Online Supplemental Material B.

In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance. Opposing the task- and work-oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment. Additionally, some clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself. Similarly, socializing and celebrations were also explicit social needs (incl., parties). This also included a subtopic of spiritual, religious, and otherwise transcendental needs (incl. meditation, prayer, religious services). Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned with informational needs more generally (e.g., seeking answers, bureaucratic information). A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel-related goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific to contact through the medical and public health system. This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly highlighted interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals). Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members. Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together or had organizational needs (e.g., housing, cleaning, and co-living). In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
